A Switching Planner for Combined Task and Observation Planning

### 2011-02-08 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/evaluation.tex
New experimental data

We have implemented our switching continual approach in the MAPSIM
environment~\cite{brenner:nebel:jaamas09},
using \system{dlib-ml}~\cite{king:2009} for belief
revision. Sequential sessions use a modified version of Fast
Downward~\cite{fast-downward}, and DT sessions use our own contingent
procedure. We also implemented a simple dual-mode replanning {\em
baseline} approach. Here, when a switching action is scheduled for
execution the DT session executes a single entropy reduction action,
that directly senses an active assumption -- I.e,. We say a fact can
be directly sensed, if there is a DTPDDL {\em sense} declaration that
mentions the fact in its precondition.  Control is then immediately
returned to a new sequential session.

We evaluate our approaches in robot exploration tasks from home and
office environments. Spatially, these consists of {\em rooms}
(office/kitchen/etc), and an underlying topological map that models
smaller areas of space, called {\em places}, and connectivity between
those. The mobile {\em robot} and {\em visual objects} inhabit the
topological space, the latter indicate the category of space they
inhabit -- E.g., Spoons are likely to be in kitchens. By examining
view cones at places for particular objects, the robot is able to: (1)
categorise space at high (room) and low (place) levels, and (2) find
objects for the user, exploiting information about object
co-occurrence and room categories for efficiency. Also, in the
presence of a person, the robot can ask them about the location of
objects.

We compare our switching planner against the {\em baseline} in several
realistic tasks, with the number of rooms ranging from 3 (12-places,
16-objects, $|$states$|$$>\sim10^{21}$) to 6 (26-places, 21-objects,
$|$states$|$ $>10^{36}$). For or experiments we model three sensors:
{\em Reliable} sensors have a $0.1$ probability of a false negative,
{\em semi-reliable} have a chance of $0.3$ of false negative and $0.1$
of false positive , and finally {\em noisy} sensors with probabilities
of $0.5$ and $0.2$ respectively. Each object class is assigned one
sensor model, so e.g. cornflakes may be harder to detect than
refrigeratos. To determine the influence of the sensor model, we
performed several experiments where we only changed the difficulty of
the target object(s). All non-target objects remain unchanged so the
planner may exploit object co-occurances with reliable objects to
compensate for the increased sensor noise.

@@

\begin{figure}[h!]
  % \centering
  % \includegraphics{dora1-time}\hfill
  % \vspace{2mm}
  \includegraphics{dora2-time}\hfill
  % \vspace{2mm}
  \includegraphics{dora3-time}\hfill
  % \vspace{2mm}
  \includegraphics{dora4-time}\hfill
  \vspace{2mm}
  % \includegraphics{dora56-time}\hfill
  % \vspace{2mm}
  % \includegraphics{dora-cat-time}\hfill
  \caption{Average runtime}
  \label{fig:results-time}
\end{figure}

\begin{figure}[h!]
  % \centering
  % \includegraphics{dora1-quality}\hfill
  % \vspace{2mm}
  \includegraphics{pomdp-quality}\hfill
  \includegraphics{dora2-quality}\hfill
  % \vspace{2mm}
  \includegraphics{dora3-quality}\hfill
  % \vspace{2mm}
  \includegraphics{dora4-quality}\hfill
  \vspace{2mm}
  % \includegraphics{dora56-quality}\hfill
  % \vspace{2mm}
  % \includegraphics{dora-cat-quality}\hfill
  \caption{Average plan costs and number of successful runs.}
  \label{fig:results-quality}
\end{figure}

We find that if sensing is reliable there is little to be gained
through DT sessions, as the greedy approach of the {\em baseline} is
sufficient. As sensing degrades contingent planning pays off.  Time
spent in DT planning increases steeply as the abstraction $\bstate_0$
becomes more refined.  That refinement seems to be paying off in terms
of the success rate, particularly for tasks $d$ and $e$. For less
refined initial configurations, the increase cost of DT
planning is compensated by a decrease in Fast Downward planning
times. The relatively high success rate irrespective of the level of
refinement in the initial configuration indicates the effectiveness of
using conditional entropy to guide abstraction refinement in our
setting.

>>>>

We have implemented our switching continual approach in the MAPSIM
environment~\cite{brenner:nebel:jaamas09},
using \system{dlib-ml}~\cite{king:2009} for belief
revision. Sequential sessions use a modified version of Fast
Downward~\cite{fast-downward}, and DT sessions use our own contingent
procedure. We also implemented a simple dual-mode replanning {\em
baseline} approach. Here, when a switching action is scheduled for
execution the DT session executes a single entropy reduction action,
that directly senses an active assumption -- i.e,. We say a fact can
be directly sensed, if there is a DTPDDL {\em sense} declaration that
mentions the fact in its precondition.  Control is then immediately
returned to a new sequential session.

We evaluate our approaches in robot exploration tasks from home and
office environments. Spatially, these consist of {\em rooms}
(office/kitchen/etc), and an underlying topological map that models
smaller areas of space, called {\em places}, and connectivity between
those. The mobile {\em robot} and {\em visual objects} inhabit the
topological space, the latter indicate the category of space they
inhabit -- e.g., Spoons are likely to be in kitchens. By examining
view cones at places for particular objects, the robot is able to: (1)
categorise space at high (room) and low (place) levels, and (2) find
objects for the user, exploiting information about object
co-occurrence and room categories for efficiency. Also, in the
presence of a person, the robot can ask them about the location of
objects.

We compare our switching planner with the {\em baseline} in several
realistic tasks, with the number of rooms ranging from 3 (12-places,
16-objects, $|$states$|$$>\sim10^{21}$) to 6 (26-places, 21-objects,
$|$states$|$ $>10^{36}$). For or experiments we model three sensors:
{\em Reliable} sensors have a $0.1$ probability of a false negative,
{\em semi-reliable} have a chance of $0.3$ of false negative and $0.1$
of false positive , and finally {\em noisy} sensors with probabilities
of $0.5$ and $0.2$ respectively. Each object class is assigned one
sensor model, so e.g. cornflakes may be harder to detect than
refrigeratos. To determine the influence of the sensor model, we
performed several experiments where we only changed the difficulty of
the target object(s). All non-target objects remain unchanged so the
planner may exploit object co-occurances with reliable objects to
compensate for the increased sensor noise.

@@

\begin{figure}[h!]
  % \centering
  % \includegraphics{dora1-time}\hfill
  % \vspace{2mm}
  \includegraphics{dora2-time}\hfill
  % \vspace{2mm}
  \includegraphics{dora3-time}\hfill
  % \vspace{2mm}
  \includegraphics{dora4-time}\hfill
  \vspace{2mm}
  \includegraphics{dora56-time}\hfill
  % \vspace{2mm}
  % \includegraphics{dora-cat-time}\hfill
  \caption{Average runtime}
  \label{fig:results-time}
\end{figure}

\begin{figure}[h!]
  % \centering
  % \includegraphics{dora1-quality}\hfill
  % \vspace{2mm}
  \includegraphics{pomdp-quality}\hfill
  \includegraphics{pomdp-solvable-quality}\hfill
  \includegraphics{dora2-quality}\hfill
  % \vspace{2mm}
  \includegraphics{dora3-quality}\hfill
  % \vspace{2mm}
  \includegraphics{dora4-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora56-quality}\hfill
  % \vspace{2mm}
  % \includegraphics{dora-cat-quality}\hfill
  \caption{Average plan costs and number of successful runs.}
  \label{fig:results-quality}
\end{figure}

We find that if sensing is reliable there is little to be gained
through DT sessions, as the greedy approach of the {\em baseline} is
sufficient. As sensing degrades contingent planning pays off.  Time
spent in DT planning increases steeply as the abstraction $\bstate_0$
becomes more refined.  That refinement seems to be paying off in terms
of the success rate, particularly for tasks $d$ and $e$. For less
refined initial configurations, the increased cost of DT
planning is compensated for by a decrease in Fast Downward planning
times. The relatively high success rate irrespective of the level of
refinement in the initial configuration indicates the effectiveness of
using conditional entropy to guide abstraction refinement in our
setting.
